Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-11 paper.Rmd
fix typo

table2_nosmooth %>%
  dplyr::select(-Model, -horizon) %>%
  knitr::kable(
    digits = 2, booktabs = TRUE, 
    caption = "Comparison of escalation model to structural extensions, using test set AUC-ROC (Replication of B\\&S Table 2)",
    label = "table2-fixed") %>%
  column_spec(2:6, width = "2cm") %>%
  pack_rows(index = c("One-month forecasts" = 1, "Six-month forecasts" = 1)) %>%
  footnote("Differences from the original B\\&S Table 2: (1) AUC-ROC values are computed on the common subset of cases, meaning that N is equal in each row; (2) AUC-ROC values are computed using original, non-smoothed ROC curves.", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

>>>>

table2_nosmooth %>%
  dplyr::select(-Model, -horizon) %>%
  knitr::kable(
    digits = 2, booktabs = TRUE, 
    caption = "Comparison of escalation model to structural extensions, using test set AUC-ROC (Replication of B\\&S Table 2)",
    label = "table2-fixed") %>%
  column_spec(2:6, width = "2cm") %>%
  pack_rows(index = c("One-month forecasts" = 1, "Six-month forecasts" = 1)) %>%
  footnote("Differences from the original B&S Table 2: (1) AUC-ROC values are computed on the common subset of cases, meaning that N is equal in each row; (2) AUC-ROC values are computed using original, non-smoothed ROC curves.", footnote_as_chunk = TRUE, threeparttable = TRUE)
```
